Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-05 paper/main.tex
backing up changes to participants, stimuli, and speech-to-text sections of materials and methods

\begin{figure} 
    \centering
        \includegraphics[width=0.4 \textwidth]{figures/FRFR}

@@

% need a summary statement...

@@

Our experimental paradigm incorporates the Annyang and Google Cloud Speech API
speech-to-text engines to automatically transcribe participants' verbal recalls
into text. This allows recalls to be transcribed in real time-- a
distinguishing feature of the experiment; in typical verbal recall experiments
the audio data must be parsed manually. (We have run a pilot experiment to
verify that the automatically transcribed recalls are sufficiently close to
human-transcribed recalls to yield reliable data.) This real-time speech
processing component of the paradigm plays an important role in Experiments
3--5.

@@

@@

>>>>

@@

@@

\begin{figure} 
    \centering
        \includegraphics[width=0.75 \textwidth]{figures/FRFR}

@@

Stimuli in our paradigm were 256 English words selected in a previous
study~\citep{ZimaEtal18}. The words all referred to concrete nouns, and were
chosen from 15 unique semantic categories: body parts, building-related,
cities, clothing, countries, flowers, fruits, insects, instruments,
kitchen-related, mammals, (US) states, tools, trees, and vegetables. We also
tagged each word according to the approximate size of the object the word
referred to. Words were labeled as ``small'' if the corresponding object was
likely able to ``fit in a standard shoebox'' or ``large'' if the object was
larger than a shoebox. Semantic categories varied in how many object sizes they
reflected (mean number of different sizes per category: 1.33; standard
deviation: 0.49). The numbers of words in each semantic category also varied
from 12 -- 28 (mean number of words per category: 17.07; standard deviation
number of words: 4.65). We also identified lexicographic features for each
word, including the words' first letters and lengths (i.e., number of letters).
Across all categories, all possible first letters were represented except for
`Q' (average number of unique first letters per category: 11; standard
deviation: 2 letters). Word lengths ranged from 3 -- 12 letters (average: 6.17
letters; standard deviation: 2.06 letters).

We assigned the categorized words into a total of 16 lists with several
constraints. First, we required that each list contained words from exactly 4
unique categories, each with exactly 4 examplars from each category. Second, we
required that (across all words on the list) at least one instance of both
object sizes were represented. On average, each category was represented in
4.27 lists (standard deviation: 1.16 lists). Aside from these two constraints,
we assigned each word to a unique list. After random assignment, each list
contained words with an average of 11.13 unique starting letters (standard
deviation: 1.15 letters) and an average word length of 6.17 letters (standard
deviation: 0.34 letters).

The above assignments of words to lists was performed once across all
participants, such that every participant studied the same set of 16 lists. We
randomized the study order of these lists across participants. For participants
in some conditions, on some lists, we also randomly varied two additional
visual features to each word: the presentation font color, and the word's
onscreen location. These attributes were assigned independently for word (and
for every participant) at the times the words were displayed onscreen. These
visual features were varied for words in all lists and conditions except for
the ``reduced'' condition (all lists), the first eight lists of the ``reduced
(early)'' condition, and the last eight lists of the ``reduced (late)''
condition. In these latter cases, words were all presented in black at the
center of the experimental computer's display.

To assign a random font color to each word, we selected three integers
uniformly and at random between 0 and 255, corresponding to the red (r), green
(g), and blue (b) color channels for that word. To assign random presentation
locations to each word, we selected two floating point numbers uniformly at
random (one for the word's horizontal $x$ coordinate and the other for its
vertical $y$ coordinate).  The bounds of these coordinates were selected to cover the entire
visible area of the display without cutting off any part of the words.  The words were shown
on 27~in (diagonal) Retina 5K iMac displays (resolution: 5120 $\times$ 2880 pixels).

@@

Our experimental paradigm incorporates the Google Cloud Speech API
speech-to-text engine~\citep{HalpEtal16} to automatically transcribe
participants' verbal recalls into text. This allows recalls to be transcribed
in real time-- a distinguishing feature of the experiment; in typical verbal
recall experiments the audio data must be parsed manually. In prior work, we
used a similar experimental setup (equivalent to the ``reduced'' condition in
the present study) to verify that the automatically transcribed recalls were
sufficiently close to human-transcribed recalls to yield reliable
data~\citep{ZimaEtal18}. This real-time speech processing component of the
paradigm plays an important role in the ``adaptive'' condition of the
experiment, as described below.
